Optimal (Multiway) Spatial Joins

### 2024-05-28 4.2.tex
4.2

Finally, we prove (3).

>>>>

Finally, we prove (3). 
For each $\bm{t'}\in  \J(R_1',...,R_{k-2}')$ and each $h \in \dcross_H(\bm{t'})$, we will identify a unique tuple $\bm{t}$ in $\J(R_1,...,R_{k-2},H,V)$ defined as follows. Let $r_i$ be the full rectangle of $r_i'$ for $i \in [k]$, and $v$ be the segment $v_\vdash$ of $\gleft(\bm{t'})$. Let $\bm{t} = (r_1,...,r_{k-2},h,v)$. Since $h$ crosses $B_{\bm{t'}}$ by the definition of $\dcross_H(\bm{t'})$, the $h\cap v$ is a point in $B_{\bm{t'}}$. 
Therefore, $h\cap v \in B_{\bm{t'}} \subseteq B_{\bm{t}}$, and $\bm{t}\in \J(R_1,...,R_{k-2},H,V)$. As a result, $\sum_{\bm{t}\in \J(R_1',...,R_{k-2}')}  |\dcross_H(\bm{t})| \leq \out$.

Similarly, for each $\bm{t'}\in  \J(R_1',...,R_{k-2}')$ and each $v \in \dcross_V(\bm{t'})$, we can identify a unique tuple $\bm{t}$ in $\J(R_1,...,R_{k-2},H,V)$ defined as follows. Let $r_i$ be the full rectangle of $r_i'$ for $i \in [k]$, and $h$ be the segment $h_\bot$ of $\gbot(\bm{t'})$. Let $\bm{t} = (r_1,...,r_{k-2},h,v)$. Since $v$ crosses $B_{\bm{t'}}$, $h\cap v \in B_{\bm{t'}} \subseteq B_{\bm{t}}$, and $\bm{t}\in \J(R_1,...,R_{k-2},H,V)$. As a result, $\sum_{\bm{t}\in \J(R_1',...,R_{k-2}')}  |\dcross_V(\bm{t})| \leq \out$.
